06_DESeqALL

### 2019-12-31 analysis/06_DESeq2_ALL.Rmd
new volcano plots

plot_grid(timingicons, timing2, nrow = 2, rel_heights = c(0.9,1))
```

>>>>

plot_grid(timingicons, timing2, nrow = 2, rel_heights = c(0.9,1))

remove2 <- plot_grid( 
          NULL,
          j , 
          k + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          l + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          m + theme(axis.title.y = element_blank(), axis.text.y = element_blank()), 
          nrow = 1, rel_widths = c(1,1.4,1,1,1))

plot_grid(removeicons, remove2, nrow = 2, rel_heights = c(0.9,1))
```
